The curious world of constructive mathematics

### 2022-09-08 algar-lecture-notes.tex
typo

\newenvironment{intro}{\begin{quote}}{\end{quote}\bigskip}

@@

\begin{ex}Classical linear algebra teaches us that every finite system of
generators of a vector space over a residue field\footnote{Constructively, the
notion of a field bifurcates into several nonequivalent notions: A nontrivial
commutative ring with unit is a \ldots
\begin{enumerate}
\item a \emph{geometric field} or \emph{discrete field} iff
every element is zero or
invertible (as in~$\QQ$ or~$\overline{\QQ}$),
\item a \emph{residue field} iff
every element which is not invertible is zero (as in the Cauchy or Dedekind
reals), and
\item a \emph{field of fractions} iff
every element which is not zero is invertible (as in the localization of the
Cauchy or Dedekind reals at the set of non-zeros).
\end{enumerate}These each have their
uses~\cite{johnstone:rings-fields-and-spectra,mulvey:repr}.}
can be thinned to a generating family in which no vector is redundant, hence to
a basis. By slightly massaging the result obtained by the double-negation
embedding, we obtain the constructive theorem that every finitely generated
vector space over a residue field does \emph{not not} possess a basis.

>>>>

\newenvironment{intro}{\begin{quote}}{\end{quote}\bigskip\noindent}

@@

\begin{ex}Classical linear algebra teaches us that every finite system of
generators of a vector space over a residue field\footnote{Constructively, the
notion of a field bifurcates into several nonequivalent notions: A nontrivial
commutative ring with unit is a \ldots
\begin{enumerate}
\item a \emph{geometric field} or \emph{discrete field} iff
every element is zero or
invertible (as in~$\QQ$ or~$\overline{\QQ}$),
\item a \emph{residue field} iff
every element which is not invertible is zero (as in the Cauchy or Dedekind
reals), and
\item a \emph{field of fractions} iff
every element which is not zero is invertible (as in the localization of the
Cauchy or Dedekind reals at the set of non-zeros or in the \emph{generic local
ring} described in Lecture~\ref{lect:generic}).
\end{enumerate}These each have their
uses~\cite{johnstone:rings-fields-and-spectra,mulvey:repr}.}
can be thinned to a generating family in which no vector is redundant, hence to
a basis. By slightly massaging the result obtained by the double-negation
embedding, we obtain the constructive theorem that every finitely generated
vector space over a residue field does \emph{not not} possess a basis.
